Congestion Control Aware Queuing

### 2019-10-17 tex/paper.tex
Improve paper a little bit

\def\tempYes{yes}
\def\tempNo{no}
\documentclass[10pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi\ifx\removeHeaders\tempNo ,anonymous\fi]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{Workshop on Buffer Sizing}{December 2-3, 2019}{Stanford, California, USA}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/traq_illustration_too_much.pdf}
\caption{If the buffer is too large, loss-based \glspl{cca} will keep a unnecessary standing queue. This queue is unnecessary since it is not generally required to achieve full link utilization. The consequences are longer \glspl{rtt} which can impair application performance and fluidity as well as Quality of Experience.}
\label{fig:tooMuch}
\end{figure}

@@

The other case we want to avoid is a persisting standing queue, as depicted in \autoref{fig:tooMuch}: In this case the buffer is too large meaning that optimal throughput is achieved but at the same time that an unnecessarily long standing queue is maintained. This oversized queue leads to \gls{rtt} being larger than necessary and can result in unresponsive applications. Furthermore, the buffer space has to be allocated in the bottleneck device and keeps the memory from serving a more useful purpose.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{{{figures/traq_intervals}}}
\caption{Illustration of the interval mechanism used by our \gls{qdisc}. The multiplier used is $\frac{1}{2}$. Each \textit{guard interval} (GI) contains one or more intervals of which the longest one is considered the \textit{longest interval} (LI). The \gls{gi} is always at least the length of the previous \gls{li} times the multiplier. A \gls{gi} ends at the first packet loss after that is after the previous \gls{li} times the multiplier.}
\label{fig:intervals}
\end{figure}

@@

We implement our \gls{qdisc} as an extension of the ``fq'' \gls{qdisc} \cite{dumazet_pkt_sched:_2013}. This means that when using our \gls{qdisc} also all features offered by fq are available. We add three configuration parameters to the \gls{qdisc}: the multiplier (default 1.25), the maximum buffer increase (default 2.0) and the maximum \gls{gi} duration (default 1.0\,s). We make the source code of our implementation freely available to enable reproducibility and encourage experimentation: \ifx\removeHeaders\tempYes\url{https://github.com/CN-TU/traq}\else{}[removed for anonymity]\fi .

@@

Next we compare our \gls{qdisc} against fq\_codel. Figure\autoref{fig:fqCodelDelayLong} shows that fq\_codel keeps the queuing delay under 5\,ms. Figure\autoref{fig:fqCodelThroughputLong} shows that keeping the queuing delay that low is detrimental for achieving full throughput when using the Cubic \gls{cca}. With our \gls{qdisc} we achieve throughput that is more than 10\% higher overall, while only slightly increasing the average delay \todo{More systematic evaluation}. In addition to Cubic, we performed experiments with Reno. Here, over a 240\,s flow of 100\,Mbit/s with a delay of 50\,ms, our \gls{qdisc} achieves more than 20\% higher throughput than fq\_codel. The average \gls{rtt} for fq\_codel is 51.13\,ms while it is 96.59\,ms for our \gls{qdisc}.

@@

We see this work as a first step towards adaptive queuing at bottlenecks and think that a promising direction for future work might be to explore the use of reinforcement learning. Such an approach would fingerprint a flow and choose the buffer size accordingly, maximizing a chosen objective such as high throughput with minimal delay.

\section*{Acknowledgements}
We thank \ifx\removeHeaders\tempYes{}Gernot Vormayr\else{}[removed for anonymity]\fi{} for providing us with the \ifx\removeHeaders\tempYes{}\texttt{py-virtnet}\else{}[removed for anonymity]\fi{} toolkit for building virtual networks.

>>>>

\def\tempYes{yes}
\def\tempNo{no}
\documentclass[10pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{Workshop on Buffer Sizing}{December 2-3, 2019}{Stanford, California, USA}

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{figures/traq_illustration_too_much.pdf}
\caption{If the buffer is too large, loss-based \glspl{cca} will keep a unnecessary standing queue. This queue is unnecessary since it is not generally required to achieve full link utilization.}
\label{fig:tooMuch}
\end{figure}

@@

The other case we want to avoid is a persisting standing queue, as depicted in \autoref{fig:tooMuch}: In this case the buffer is too large meaning that optimal throughput is achieved but at the same time that an unnecessarily long standing queue is maintained. This oversized queue leads to \gls{rtt} being larger than necessary and can result in unresponsive applications and reduced Quality of Experience. Furthermore, the buffer space has to be allocated in the bottleneck device and keeps the memory from serving a more useful purpose.

@@

\begin{figure}[h]
\includegraphics[width=\columnwidth]{{{figures/traq_intervals}}}
\caption{Illustration of the interval mechanism used by our \gls{qdisc} with a multiplier of $\frac{1}{2}$. Each \textit{guard interval} (GI) contains one or more intervals of which the longest one is considered the \textit{longest interval} (LI). The \gls{gi} is always at least the length of the previous \gls{li} times the multiplier. A \gls{gi} ends at the first packet loss after that is after the previous \gls{li} times the multiplier.}
\label{fig:intervals}
\end{figure}

@@

We implement our \gls{qdisc} as an extension of the ``fq'' \gls{qdisc} \cite{dumazet_pkt_sched:_2013}. This means that when using our \gls{qdisc} also all features offered by fq are available. We add three configuration parameters to the \gls{qdisc}: the multiplier (default 1.25), the maximum buffer increase (default 2.0) and the maximum \gls{gi} duration (default 1.0\,s). We make the source code of our implementation freely available to enable reproducibility and encourage experimentation: \url{https://github.com/CN-TU/traq}.

@@

Next we compare our \gls{qdisc} against fq\_codel. Figure\autoref{fig:fqCodelDelayLong} shows that fq\_codel keeps the queuing delay under 5\,ms. Figure\autoref{fig:fqCodelThroughputLong} shows that keeping the queuing delay that low is detrimental for achieving full throughput when using the Cubic \gls{cca}. With our \gls{qdisc} we achieve throughput that is more than 10\% higher overall, while only slightly increasing the average delay. In addition to Cubic, we performed experiments with Reno. Here, over a 240\,s flow of 100\,Mbit/s with a delay of 50\,ms, our \gls{qdisc} achieves more than 20\% higher throughput than fq\_codel. The average \gls{rtt} for fq\_codel is 51.13\,ms while it is 96.59\,ms for our \gls{qdisc}.

@@

We see this work as a first step towards adaptive queuing at bottlenecks. An interesting further improvement could be to not statically initialize the buffer with a constant 100 packets but instead use experience from previous flows. Moreover, we think that a promising direction for future work might be to explore the use of reinforcement learning. Such an approach would fingerprint a flow and choose the buffer size accordingly, maximizing a chosen objective such as high throughput with minimal delay.

\section*{Acknowledgements}
We thank Gernot Vormayr for providing us with a pre-release version of the \texttt{py-virtnet} toolkit for building virtual networks.
